Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Background section summary

>>>>

This section will dive into the state-of-the-art use of city reconstruction methods within the research field of urban design.
The first section will present the motivations for the digitization of urban planning, as well as the most common programs and tools in this area, which are after all not very commonly used in the practise of urban design due to the failure in being able to reflect the unique workspace of urban designers.
The Related work section will present a brief history of the field of OpenStreetMap data qualification, and present the research papers whose methods are at the foundation of this project.
